---
title: "Ideal Point Estimation of Voters Using Cast Vote Records"
author: "Mason Reece"
date: today
date-format: long
bibliography: "references.bib"
execute: 
  echo: false
  cache: true
format: 
  html:
    toc: true
    embed-resources: true
  pdf:
    toc: false
    number-sections: false
---

```{r}
#| message: false
#| warning: false

library(targets)
library(tarchetypes)
library(tidyverse)

```

# Data

I remove all uncontested races, and all races where a voter could select more than one candidate (although see @sec-extensions). In addition, I subset my data to a random selection of 25,000 voters in Colorado, to make computation tractable. Colorado has some of the best coverage of any state in the data -- nearly every county is represented and the state already has a decent partisan and demographic mix so that I can think of it as a good benchmark for how the model would perform in every other state.

# Model Specification

## Item Response Theory

## Binomial Outcome

To start, I follow the previous literature on this topic @lewis2001 by only focusing on binary choices. That research achieved that by only focusing on propositions, which are inherently encoded as Yes/No choices. However, I want to make use of the full set of my data, so I create a variable `choice_rep` that is a binary 1/0 for if the voter has selected the Republican candidate in the race. This choice means that all ideal points on the right side of the scale will indicate greater likelihood to select the Republican candidate (and thus naturally map to the left/right US political party scale). In theory, a similar variable for the choice of the Democrat would have achieved basically the same results (just with the scale flipped).

### Rasch Model

I start by fitting a simple Rasch model. First, I do this for a random county in Colorado, Adams County, then for the whole state. I estimate the following Bernoulli model using `brms` . All models are run for 4 chains, with 1000 warm-up iterations and then 1000 sampling iterations. Trace plots are too numerous to display, so @fig-binomial-rhats instead plots the $\hat{R}$ value for every parameter in the model. As can be seen, all $\hat{R}$ values are extremely close to 1, indicating the model has converged well. This is true for all the model specifications in this section (also shown in @fig-binomial-rhats).

```{r}
#| eval: false
#| echo: true

bf(choice_rep ~ county_name + (1 | office/district) + (1 | cvr_id))
```

```{r}
#| label: fig-binomial-rhats
#| fig-cap: Comparison of $\hat{R}$ values

tar_read(plot_rhat_comparison)
```

Rasch models treat each race as equally important in determining the ideal point of a voter, so really we can only look at those ideal points. I randomly select 10 voters and plot their estimated ideal points in @fig-binomial-rasch-voters-adams.

```{r}
#| label: fig-binomial-rasch-voters-adams
#| fig-cap: Ideal Point Estimations for Adams County, Colorado
#| fig-subcap: Binomial, Partisans, Rasch
#| warning: false

tar_read(plot_rasch_binomial_partisans_colorado_adams_voters)
```

### 2PL Model, Constrained Discrimination

## Categorical Outcomes

# Potential Extensions {#sec-potential-extensions}

Scaling latent space together from this data and the DIME scores could be Scaling Data from Multiple Sources by Ted Enamorado 1, Gabriel López-Moctezuma2 and Marc Ratkovic.

Ends Against the Middle: Measuring Latent Traits when Opposites Respond the Same Way for Antithetical Reasons by JBrandon Duck-Mayr 1 and Jacob Montgomery. Different from just including a second dimension to explain responses. But maybe I should just say that we should include additional dimensions.

Nonparametric Ideal-Point Estimation and Inference Alexander Tahk

Extension to modeling races with magnitude \> 1

# Nov 11 Update

```{r}
#| label: fig-adams-2pl-offices
#| fig-cap: Partisans, Binomial, 2PL -- Adams County, Colorado
#| eval: true
#| echo: false

tar_read(plot_2pl_binomial_partisans_colorado_adams_offices)

```

As shown in @fig-adams-2pl-offices, each office is not very discriminatory. The reason for this is that most people are straight-ticket voters, and so there is mostly no variation among voters. Maybe could focus only on people who actually split a ticket, or perhaps just by including more people in the same we would be able to recover more of an effect here.

\newpage

# References
